Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-30 thesis/experiment.tex
Subsection, not subsubsection
Put into enumerable list vs subsections
Bit more content in the tools section

\subsection{Hub/Managed Router}

@@

\subsection{Tor Software}

\subsection{'tcpdump' Software}

@@

\subsection{Weka Software}

@@

\subsection{VirtualBox Software}

@@

\subsection{Ruby Software}

Ruby is an object orientated, dynamic programming language which is useful for
rapid prototyping and as such has been used to automate the simulation
described in this experiment \parencite{:2010uq}.

(I used it because it is a language that is fast to develop in and I am
familiar with it)

\subsection{Ubuntu Linux Software}

The Ubuntu Linux operating system is freely available Linux operating system
available for desktop personal computers.

\cite{:2010ly}

\subsection{Selenium Software}

@@

\subsection{Firefox Software}

Firefox is a web browser developed by the Mozilla organization and freely
available for most desktop personal computers \parencite{mozilla}. It's strong
standards compliance \parencite{Hammond:2010fk} and popularity
\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
candidate for this experiment.

\subsection{OpenSSH Software}

OpenSSH is a freely available suite of connectivity tools
\parencite{:2010zr,:ve} that supports remote command execution
\parencite{Tucker:2010ly}.

\cite{:2010zr}

\subsection{Apache Software}

The Apache web server is the most prevalent web server used on the internet
\parencite{2010:dq}.  \cite{:qf}

\subsection{Sinatra Software}

@@

@@

\subsubsection{Standard OS Installation Procedure}
\label{section:os_install}

>>>>

\begin{enumerate}
  \item Hub/Managed Router

@@

  \item 'tcpdump' Software

@@

  \item Tor Software

  The Tor software is available on a number of operating systems and the Tor
  project makes packages available for the Ubuntu operating system.

  \item Weka Software

@@

  \item VirtualBox Software

@@

  \item Ruby Software

  Ruby is an object orientated, dynamic programming language which is useful for
  rapid prototyping and as such has been used to automate the simulation
  described in this experiment \parencite{:2010uq}. It is supported by the
  Selenium framework and so can be used to automate a web browser and includes
  community developed plug-in modules called gems that provide functionality for
  monitoring automated software and performing test sequences.

  \item Ubuntu Linux Software

  The Ubuntu Linux operating system is freely available Linux operating system
  available for desktop personal computers \parencite{:2010ly}. It comes
  packaged with the 'tcpdump' software and can be configured in a reliable and
  consistent way with typical set of POSIX tools and the 'apt-get' package
  manager. \parencite{Pereira:2011uq}.

  \item Selenium Software

@@

  \item Firefox Software

  Firefox is a web browser developed by the Mozilla organization and freely
  available for most desktop personal computers \parencite{Foundation:2011fk}.
  It's strong standards compliance \parencite{Hammond:2010fk} and popularity
  \parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
  candidate for this experiment.

  \item OpenSSH Software

  OpenSSH is a freely available suite of connectivity tools
  \parencite{:2010zr,:ve} that supports remote command execution
  \parencite{Tucker:2010ly, :2010zr}.

  \item Apache Software

  The Apache web server is the most prevalent web server used on the internet
  \parencite{2010:dq}. Details about apache go here \parencite{:qf}.

  \item Sinatra Software

@@

\end{enumerate}

@@

\subsection{Standard OS Installation Procedure}
\label{section:os_install}
